Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-12 volunteer-clouds-ieee-ci-si.tex
homogeneizar cómo escribimos Web Workers

In this sense, in this paper we propose {\sf NodIO}, a cloud or metal
based 
volunteer evolutionary computing system based on the {\sf NodEO}
library, whose architecture 
has been developed using JavaScript on the client as well as the
server sides. 
All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} architecture has two tiers:\begin{enumerate}
\item A REST server, that is, a server that includes several {\em
  routes} %remote requests suena raro, propongo algo como: remote
          %procedures o web interfaces [jj] changed to routes, its
          %proper name.
  that can be called for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it, and {\em information} related
  to performance and state of the experiments. It also performs logging
  duties, but is basically a very lightweight and high performance
  data store \cite{jj:idc:lowcost}.
  The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found.
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when solution is found or, as we have done in this paper,
  using WebWorkers, which run in the background even if the webpage or
  browser tab with the experiment is not currently on focus.
\end{enumerate}

@@

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it is a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmic variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two WebWorkers. It is a matter of a single click to
open more tabs in the browser, giving more WebWorkers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

>>>>

In this sense, in this paper we propose {\sf NodIO}, a cloud or metal
based 
volunteer evolutionary computing system based on the {\sf NodEO}
library, whose architecture 
has been developed using JavaScript on the client as well as the
server sides. 
All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} architecture has two tiers:\begin{enumerate}
\item A REST server, that is, a server that includes several {\em
  routes} %remote requests suena raro, propongo algo como: remote
          %procedures o web interfaces [jj] changed to routes, its
          %proper name.
  that can be called for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it, and {\em information} related
  to performance and state of the experiments. It also performs logging
  duties, but is basically a very lightweight and high performance
  data store \cite{jj:idc:lowcost}.
  The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found.
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when solution is found or, as we have done in this paper,
  using Web Workers, which run in the background even if the webpage or
  browser tab with the experiment is not currently on focus.
\end{enumerate}

@@

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it is a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmic variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two Web Workers. It is a matter of a single click to
open more tabs in the browser, giving more Web Workers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.
